### 2019-10-26 README.Rmd
updated talking points

- Can we talk about the LIME assumptions?
- What names should I give to the diagnostic plots?
- Could you help me with the interpretation of the default LIME explanations?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

@@

- Treats?

@@

- draft paper
- start organizing literature review paper

>>>>

@@

@@

- draft paper
- start organizing literature review paper
- set up dissertation R markdown document
